Embedding to Reference t-SNE Space Addresses Batch Effects in Single-Cell Classification

### 2019-08-13 paper/policar2019-tsne-embedding.tex
Reformat latex

\begin{figure}[htb]
\includegraphics[width=\textwidth]{figures/transform_pancreas.pdf}
\caption{Embedding of pancreatic cells from Baron \etal~\cite{baron2016} and
cells from the same tissue from Xin \etal.~\cite{xin2016}. Just like in
Fig.~\ref{fig:transform_brain} the vast majority of the cells from the secondary
data set were correctly mapped to the same-typed cluster of reference
cells.}\label{fig:transform_pancreas}
\end{figure}

>>>>

\begin{figure}[htb]
  \includegraphics[width=\textwidth]{figures/transform_pancreas.pdf}
  \caption{Embedding of pancreatic cells from Baron \etal~\cite{baron2016} and
  cells from the same tissue from Xin \etal.~\cite{xin2016}. Just like in
  Fig.~\ref{fig:transform_brain} the vast majority of the cells from the
  secondary data set were correctly mapped to the same-typed cluster of
  reference cells.}
  \label{fig:transform_pancreas}
\end{figure}
